Elephant Seal Age JAE Intraspecific Variation

### 2023-12-08 paper/paperv3.qmd
Fixing the recruitment problem seals

sealdat <- read_csv(here::here("data/raw/128L pull 2023_12_05.csv"), 
                    show_col_types = FALSE) %>% 
  mutate(observed = if_else(observed == "B", "Breeder", "Non-breeder"), 
         observed_int = if_else(observed == "Breeder", 1, 0), 
         pup_survived = pupseeneveragain > 0) %>% 
  filter(age > 3, 
         year > 1987) %>% 
  mutate(across(c(animalID, year), factor),
         age10 = age / 10)

# 17 observations where pup recruited but did not survive
problem_children <- filter(sealdat, puprecruited == 1 & !pup_survived)

sealdat <- anti_join(sealdat, problem_children, by = c("animalID", "pupID"))
```

@@

pupsex_cap <- str_glue("The results from offspring sex ratio analyses. In the model, the random effect variance of animal id is {format_signif(VarCorr(pup_sex_mod)$animalID, 3)} and of year was {format_signif(VarCorr(pup_sex_mod)$year, 3)}. 
```

>>>>

sealdat <- read_csv(here::here("data/raw/128L pull 2023_12_05.csv"), 
                    show_col_types = FALSE) %>% 
  mutate(observed = if_else(observed == "B", "Breeder", "Non-breeder"), 
         observed_int = if_else(observed == "Breeder", 1, 0), 
         pup_survived = pupseeneveragain > 0) %>% 
  filter(age > 3, 
         year > 1987) %>% 
  mutate(across(c(animalID, year), factor),
         age10 = age / 10)
```

@@

pupsex_cap <- str_glue("The results from offspring sex ratio analyses. In the model, the random effect variance of animal id is {format_signif(VarCorr(pup_sex_mod)$animalID, 3)} and of year was {format_signif(VarCorr(pup_sex_mod)$year, 3)}.") 
```
